Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-21 src/ms.tex
adding to appendix

\edit1{Here we consider the possibility that there is only one astrophysical overdensity in the true \teff–\prot distribution, the long-period pile-up, and other features in the observed \teff–\prot distribution appear at period harmonics of this feature due to the difficult problem of reliable, automated rotation period measurement for large samples of stars. Figure~\ref{fig:harmonic} shows a Gaussian kernel density estimation of the \lamostmcq \teff–\prot distribution for stars with \logg~$>$~4.1. The short-period pile-up is observed in this sample, particularly for \teff~$>$~6000~K. We found through inspection a constant Rossby curve that traces the long-period pile-up. Taking this curve and dividing the periods by factors of 2 and 3, we find that neither resulting curve satisfactorily threads the short-period pile-up, though they both bracket the feature seen through density estimation. We interpret this as evidence that the short-period pile-up is not simply due to measurement error, although we have not definitively ruled out that scenario.}

>>>>

\edit1{Here we consider the possibility that there is only one astrophysical overdensity in the true \teff–\prot distribution, the long-period pile-up, and other features in the observed \teff–\prot distribution appear at period harmonics of this feature due to the difficult problem of reliable, automated rotation period measurement for large samples of stars. Figure~\ref{fig:harmonic} shows a Gaussian kernel density estimation of the \lamostmcq \teff–\prot distribution for stars with \logg~$>$~4.1. The short-period pile-up is observed in this sample, particularly for \teff~$>$~6000~K. We found through inspection a constant Rossby curve that traces the long-period pile-up. Taking this curve and dividing the periods by factors of 2 and 3, we find that neither resulting curve satisfactorily matches the short-period pile-up, though they both bracket the feature seen through density estimation. We interpret this as evidence that the short-period pile-up is not simply due to measurement error, although we have not definitively ruled out that scenario.}

\edit1{We also note that the short-period pile-up is not as prominent in the \lamostsan sample, compared to the \lamostmcq sample (see the rightmost panels of Figure~\ref{fig:xmatch}). The differences between the \citet{McQuillan2014} and \citet{Santos2021} catalogs may provide an explanation for this observation: the latter catalog contains a much larger number of detections at longer rotation periods. The higher sensitivity to more slowly rotating stars within the \citet{Santos2021} may then make the short-period pile-up appear weaker relative to the long-period pile-up, as expected since open cluster obsbervations suggest that the short-period pile-up can not be a long-lived feature.}
